\chapter{Dissemination of Work}

\section*{Publications (4 Published \& 5 In preparation)}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
2018: \textbf{Reinforcement learning produces dominant strategies for
the Iterated Prisoner's Dilemma.} Marc Harper, Vincent Knight, Martin
Jones, Georgios Koutsovoulos, Nikoleta E. Glynatsi, Owen Campbell -
\href{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0188046}{PLOS
One} -
\href{https://arxiv.org/abs/1707.06307}{Preprint arXiv:1707.06307}
\item
2018: \textbf{An evolutionary game theoretic model of rhino horn
devaluation.} Nikoleta E. Glynatsi, Vincent Knight, Tamsin Lee.
\href{https://www.sciencedirect.com/science/article/pii/S0304380018303260}{Ecological
Modelling} -
\href{https://arxiv.org/abs/1712.07640}{Preprint arXiv:1712.07640}
\item
2017: \textbf{Evolution reinforces cooperation with the emergence of
self-recognition mechanisms: an empirical study of the Moran process
for the Iterated Prisoner's dilemma.} Vincent Knight, Marc Harper,
Nikoleta E. Glynatsi, Owen Campbell -
\href{https://journals.plos.org/plosone/article/comments?id=10.1371/journal.pone.0204981}{PLOS
ONE} -
\href{https://arxiv.org/abs/1707.06920}{Preprint arXiv:1707.06920}
\item
2016: \textbf{An open framework for the reproducible study of the
Iterated prisoner's dilemma.} Vincent Knight, Owen Campbell, Marc
Harper et al -
\href{https://openresearchsoftware.metajnl.com/articles/10.5334/jors.125/}{Journal
of Open Research Software}
\end{enumerate}

\textsc{In preparation}

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
\item 2019: \textbf{Properties of Winning Iterated Prisoner's Dilemma Strategies.} Nikoleta E. Glynatsi, Vincent A. Knight and Marc Harper -
In preparation to be submitted - \href{https://arxiv.org/abs/2001.05911}{Preprint arXiv:2001.05911}
\item 2019: \textbf{A bibliometric study of research topics, collaboration and influence in the field of the Iterated Prisoner's Dilemma.}
Nikoleta E. Glynatsi and Vincent A. Knight -
Submitted to Palgrave Communications - \href{https://arxiv.org/abs/1911.12112}{Preprint arXiv:1911.06128}
\item 2019: \textbf{Game Theory and Python: An educational tutorial to game
theory and repeated games using Python.} Nikoleta E. Glynatsi and Vincent A. Knight -
Submitted to the Journal of Open Source Education - Available on GitHub
\href{https://github.com/Nikoleta-v3/Game-Theory-and-Python}{Nikoleta-v3/Game-Theory-and-Python}
\item 2019: \textbf{A theory of mind: Best responses to memory-one strategies.
The limitations of extortion and restricted memory.} Nikoleta E. Glynatsi and Vincent A. Knight -
Submitted to Scientific Reports Nature -
\href{https://arxiv.org/abs/1911.12112}{Preprint arXiv:1911.12112}
\item 2019: \textbf{Recognising and evaluating the effectiveness of extortion in
the Iterated Prisoner's Dilemma.} Vincent Knight, Marc Harper, Nikoleta E. Glynatsi,
Jonathan Gillard -
In preparation to be submitted -
\href{https://arxiv.org/abs/1904.00973}{Preprint arXiv:1904.00973}
\end{enumerate}

\section*{Talks \& Posters}

\textsc{Invited Talks (Keynotes)}
\begin{itemize}
	\item How does a smile make a difference?, PyCon UK, Cardiff, 2018.
	\item The Fallacy of Meritocracy, PyCon Balkan, Belgrade, 2019.
\end{itemize}

\textsc{Others}
\begin{itemize}
\item Accessing open research literature with Python - PyCon Namibia, Namibia 2017.
\item Writing tests for research software - PyCon Namibia, Namibia 2017.
\item Optimisation of short memory strategies in the Iterated Prisoners Dilemma - Wales Mathematics Colloquium, Gregynog Hall 2017.
\item PIP INSTALL AXELROD (\textbf{poster}) - Euroscipy, Erlangen Germany 2017.
\item Arcas: Using Python to access open research literature - Euroscipy, Erlangen Germany 2017.
\item A trip to earth science with python as a companion - PyConUK, Cardiff 2017.
\item The power of memory (\textbf{poster}) - SIAM UKIE Annual Meeting, Southampton 2018.
\item Rhinos with a bit of Python - PyConNA, Namibia 2018.
\item Memory size in the Prisoners Dilemma - Wales Mathematics Colloquium, Gregynog Hall 2018.
\item Memory size in the Prisoners Dilemma - SIAM UKIE National Student Chapter, Bath University 2018.
\item Stability of defection, optimisation of strategies and testing for extortion in the Prisoner's Dilemma (\textbf{poster}) - STEM for Britain, London 2019.
\item Stability of defection, optimisation of strategies and testing for extortion in the Prisoner's Dilemma - 18th International Conference on Social Behaviour, Sedona, Arizona 2019.
\item An introduction to Time Series - Joint workshop between CUBRIC \& Mathematics Departments, Cardiff 2019.
\end{itemize}

\section*{Software development}

\begin{itemize}
\item \href{https://github.com/ArcasProject/Arcas}{Arcas}, an open source
package designed to help users collect academic articles' metadata from
various prominent journals and pre print serves.
\textbf{Contribution:} Main developer.

\item \href{https://github.com/Axelrod-Python}{Axelrod-Python
library}, an open source framework decided to the study of the
Iterated Prisoner's Dilemma.
\textbf{Contributions:} Implementation of spatial tournaments functionality,
	implementation/addition of strategies (from the literature) to the library,
	reviewing of code contributed by other contributors.

\item \href{https://www.sympy.org/en/index.html}{SymPy},
a Python library for symbolic mathematics.
\textbf{Contributions:} Implementation of Dixon's and Macaulay's resultants
which were developed for my manuscript ``A theory of mind: Best responses to
memory-one strategies. The limitations of extortion and restricted memory''.

\item\href{https://pandas.pydata.org}{Pandas}, an open source library providing
high-performance, easy-to-use data structures and data analysis tools.
\textbf{Contribution:} Fix bug which converted NaN values to strings.
\end{itemize}